---
title: "ggplot"
author: "Syed Faraz Ali"
date: "9/22/2018"
output: html_document
---

## Loading the tidyverse packages 

```{r message = FALSE}
library(dplyr)
library(purrr)
library(tidyr)
library(readr)
library(ggplot2)
library(tibble)
```

## The mpg data frame 

If we need to be explicit about where a function (or dataset) comes from, we'll use the special form package::function(). For example, ggplot2::ggplot() tells you explicitly that we're using the ggplot() function from the ggplot2 package.
```{r}
ggplot2 :: mpg 

mpg

```

## Creating a ggplot 

```{r}
ggplot(data = mpg) + 
        geom_point(mapping = aes(x = displ, y = hwy))
```


Let's turn this code into a reusable template for making graphs with ggplot2. To make a graph, replace the bracketed sections in the code below with a dataset, a geom function, or a collection of mappings.

```{r eval = FALSE}
ggplot(data = <DATA>) + 
  <GEOM_FUNCTION>(mapping = aes(<MAPPINGS>))
```

## Practicing ggplot

Run ggplot(data = mpg). What do you see?

```{r}
ggplot(data = mpg)
```


How many rows are in mpg? How many columns?

```{r}
dim(mpg)
```


What does the drv variable describe? Read the help for ?mpg to find out.

```{r}
help(mpg)
```


Make a scatterplot of hwy vs cyl.

```{r}
ggplot(data = mpg) + 
        geom_point(mapping = aes(x = cyl, y = hwy))
```




What happens if you make a scatterplot of class vs drv? Why is the plot not useful?






